\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
added a few references

Given data $X$ and associated labels $Y$
taking values $y \in {\cal Y} = \{s,
b_{i=1...k} \}$ where $s$ is the signal class and $b_{i=1...k}$ are
the background classes, the probability density of the data
can be written as a mixture
\begin{equation}
p(X) = \pi_s p(X|Y=s) + \sum_{i=1}^{k} \pi_{b_i} p(X | Y=b_i),
\end{equation}
where $\pi_{y}$ represents the prior for the signal or a given
background, and $p(X|Y)$ is the conditional distribution of the data
for the signal or a given background. Systematic uncertainties can
affect this distribution in the following ways \glnote{add references}:
\begin{itemize}
\item Uncertainties on the priors $\pi_{y}$.  These arise from
  uncertainties on the rates we expect a given process to occur as
  predicted from theoretical calculations or from alternative
  measurements of the rate of a given class.

@@

Systematic uncertainties are parameterized by nuisance parameters in the
statistical analysis of data \glnote{add references}.  Nuisance parameter often,
though not always, have a suitable prior coming from alternative measurements in
data.  For instance, the average measured energy of an electron in simulation
may be compared with those in data using a relatively pure sample of $Z$ boson
decays to electrons.  The average measured electron energy can not be measured
without uncertainty, and the measured uncertainty can be used in other analyses
to estimate the uncertainty deriving from our imperfect knowledge of the
electron's energy.  A nuisance parameter is assigned to the electron energy
uncertainty, which controls the variation of the electron energy in the
statistical analysis of data.  Nuisance parameters are typically, though not
always, constrained by a suitable prior, e.g. a Gaussian distribution with a
standard deviation equal to the measured uncertainty. \glnote{... and
accordingly, we want to build a classifier independent on the nuisance
parameter, as a way to be independent of the corresponding systematics.}

>>>>

Given data $X$ and associated labels $Y$
taking values $y \in {\cal Y} = \{s,
b_{i=1...k} \}$ where $s$ is the signal class and $b_{i=1...k}$ are
the background classes, the probability density of the data
can be written as a mixture
\begin{equation}
p(X) = \pi_s p(X|Y=s) + \sum_{i=1}^{k} \pi_{b_i} p(X | Y=b_i),
\end{equation}
where $\pi_{y}$ represents the prior for the signal or a given
background, and $p(X|Y)$ is the conditional distribution of the data
for the signal or a given background. Systematic uncertainties can
affect this distribution in the following ways \citep{sinervo2003definition,bohm2010introduction}:
\begin{itemize}
\item Uncertainties on the priors $\pi_{y}$.  These arise from
  uncertainties on the rates we expect a given process to occur as
  predicted from theoretical calculations or from alternative
  measurements of the rate of a given class.

@@

Systematic uncertainties are parameterized by nuisance parameters in the
statistical analysis of data (see e.g., \citep{bohm2010introduction,cowan2011asymptotic}).  Nuisance parameter often,
though not always, have a suitable prior coming from alternative measurements in
data.  For instance, the average measured energy of an electron in simulation
may be compared with those in data using a relatively pure sample of $Z$ boson
decays to electrons.  The average measured electron energy can not be measured
without uncertainty, and the measured uncertainty can be used in other analyses
to estimate the uncertainty deriving from our imperfect knowledge of the
electron's energy.  A nuisance parameter is assigned to the electron energy
uncertainty, which controls the variation of the electron energy in the
statistical analysis of data.  Nuisance parameters are typically, though not
always, constrained by a suitable prior, e.g. a Gaussian distribution with a
standard deviation equal to the measured uncertainty. \glnote{... and
accordingly, we want to build a classifier independent on the nuisance
parameter, as a way to be independent of the corresponding systematics.}
